---
title: "04-assign-ses"
author: "JJayes"
date: "08/12/2021"
output: html_document
---

```{r}
library(tidyverse)
```

## Purpose

I'm interested in geographic homogeneity among residents of Stockholm in 1909. 

The Stockholm city archive have got data on individuals from 1909 with name, occupation, and residential address.

We can therefore have a look at think kinds of occupational segmentation that occurs. We also have data on firm location in a similar year. We can look at who lives furthest from the nice areas and such. 

What is the reason for doing this? Data is accessible, looks really fun - a nice ML problem that will be fun to get right.

### Process

I have scraped the data on the residents of stockholm in 1909. What I need to do now is assign the occupations - written as strings - to SES scores. 

I have found I think a clever way to do this. Can use the 1910 census data as training data for the ML model. 

Process census data and Mantalslängder data. 

### Read in data

```{r}
df <- read_rds(here::here("data", "df_occstring_occhisco.rds"))

df %>% 
  count(OCCHISCO, sort = T)
```

What do we do about missing hisco codes??

```{r}
df %>% 
  filter(OCCHISCO == 99999)
```

Big chunk - maybe exclude them?!

### Assign ses to training data

```{r}
library(hisco)


df <- df %>% 
  mutate(ses = hisco_to_ses(OCCHISCO))

df %>% 
  filter(!is.na(ses)) %>% 
  count(ses, OCCSTRNG, sort = T)

```


### Try with the ML model on this data alone

```{r}
df_mod <- df %>% 
  filter(!is.na(ses)) %>% 
  select()
```

